Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
missing verb (thanks Gilles)
Compress bibliography to a single page
If necessary, a sectionbib argument to natbib saves an additional
one or two lines.
page number for gorilla quote

Our rule of thumb is that user code should not be tied to \sklearn -- which is a
\textit{library}, and not a \textit{framework}. This principle indeed avoids a
well-known problem with object-oriented design, which is that users wanting a
``banana'' should not get ``a gorilla holding the banana and the entire jungle''
(Joe~Armstrong, interviewed by \citealp{seibel2009coders}). That is, programs
using \sklearn should be easily reusable with other machine learning toolkits or
in other contexts, because they don't need to be intimately tied to it.

@@

To facilitate the adoption and the distribution of \sklearn,
the set of external dependencies is kept to a bare minimum:
only Python, NumPy and SciPy are required for a functioning installation.
Binary distributions of these are available for the major platforms.
Visualisation functionality depends on Matplotlib \citep{hunter2007matplotlib}
and/or Graphviz \citep{gansner2000},
but neither is required to do machine learning.
When feasible, external libraries are integrated into the codebase.
In particular, modified versions of \textsf{LIBSVM} and \textsf{LIBLINEAR}
\citep{chang2011libsvm,fan2008}, both written in C{}\verb!++! and wrapped using
Cython modules.

@@

\bibliographystyle{plainnat}
\DeclareRobustCommand{\VAN}[3]{#3}
\bibliography{paper}

>>>>

Our rule of thumb is that user code should not be tied to \sklearn -- which is a
\textit{library}, and not a \textit{framework}. This principle indeed avoids a
well-known problem with object-oriented design, which is that users wanting a
``banana'' should not get ``a gorilla holding the banana and the entire jungle''
(J.~Armstrong, cited by \citealp[p.~213]{seibel2009coders}).  That is, programs
using \sklearn should be easily reusable with other machine learning toolkits or
in other contexts, because they don't need to be intimately tied to it.

@@

To facilitate the adoption and the distribution of \sklearn,
the set of external dependencies is kept to a bare minimum:
only Python, NumPy and SciPy are required for a functioning installation.
Binary distributions of these are available for the major platforms.
Visualisation functionality depends on Matplotlib \citep{hunter2007matplotlib}
and/or Graphviz \citep{gansner2000},
but neither is required to do machine learning.
When feasible, external libraries are integrated into the codebase.
In particular, modified versions of \textsf{LIBSVM} and \textsf{LIBLINEAR}
\citep{chang2011libsvm,fan2008}, both written in C{}\verb!++!,
and wrapped using Cython modules, are shipped with \sklearn.

@@

\bibliographystyle{abbrvnat}
\DeclareRobustCommand{\VAN}[3]{#3}
\bibliography{paper}
